Data-driven Reduction of Multiscale Stochastic Dynamical Systems \thanks{This work was supported by ....}

### 2014-08-18 reducible_SDE/paper/SIADS_draft.tex
added small edits to reducible SDE paper

\usepackage{subcaption}

@@

\author{TeX Production\thanks{Society for Industrial and
Applied Mathematics, Philadelphia, Pennsylvania. 
(\email{multimedia@siam.org}). Questions, comments, or corrections
to this document may be directed to that email address.}}

@@

TODO: change ``curvature'' in figure to ``nonlinearity'' in $\sigma_{kernel}$
TODO: emphasize that if $\delta t$ is too large, then data does not look Gaussian
TODO: change strip to look different than other data
%\begin{figure}
%\includegraphics[width=\textwidth]{schematic}
%\caption{Illustration of how to choose $\delta t$ and $\sigma_{kernel}$ appropriately. The data shows the evolution of the ``fast'' variable at a fixed value of the ``slow'' variable.  We must choose both parameters so that the curvature effects and other nonlinearities are negligable. }
%\label{fig:schematic}
%\end{figure}

>>>>

\usepackage{graphicx}
%\usepackage{subcaption}
%\usepackage{epstopdf}

@@

\author{Carmeline J. Dsilva \and Ronen Talmon \and C. William Gear \and Ronald R. Coifman \and Ioannis G. Kevrekidis}

@@

TODO: change ``curvature'' in figure to ``nonlinearity'' in $\sigma_{kernel}$
TODO: emphasize that if $\delta t$ is too large, then data does not look Gaussian
TODO: change strip to look different than other data

\begin{figure}
\includegraphics[width=\textwidth]{schematic.eps}
\caption{Illustration of how to choose $\delta t$ and $\sigma_{kernel}$ appropriately. The data shows the evolution of the ``fast'' variable at a fixed value of the ``slow'' variable.  We must choose both parameters so that the curvature effects and other nonlinearities are negligable. }
\label{fig:schematic}
\end{figure}
